\section*{Guidelines}

During the labs, you have seen how to handle inter-task communication, resource sharing, synchronisation, ...
Use this knowledge in a clever way.\\

We ask you to work remotely, you don't need physical access to the device to contribute.
We advise you to use Microsoft Teams as you all already have an account and you can use the Remote Desktop Control feature to compile and run code from a distance.
If for some reason that doesn't suit you, keep in mind that you only need to share the \textit{main.c} file to code.
A simple Pastebin\footnote{\url{https://pastebin.com/}} might do the trick. \\

Start by making a list of all the task that you need. Then use timing diagrams, block diagrams, state machines or other operating/functional schemes to share your ideas with your team. You should also use the logic analyzer to understand how the RTOS schedules tasks in your code. \\


\section*{Deliverables}

You need to submit the following elements to us through the UV: 
\begin{itemize}
	\item the \texttt{main.c} file  of your project (only this file). We will be checking this, so make sure you place some comments in your code!  
	\item a picture of your PSoC with the \texttt{populationCntr} at the end of the game; 
	\item A small report (maximum five pages), containing the design of your code, as well as a few traces obtained with your logic analyzer that illustrate what happens at critical events in your code (for example when the game releases a clue, a random contamination, etc.) Comment those logic analyzer traces so that we can understand what happens easily (e.g. specify the state that each task is in at each point in time). 
\end{itemize}
Join all of these into a single .zip file before uploading on the UV. 

\begin{flushright}
\section*{Good luck!}
\end{flushright}
