In order  for you to work remotely, we changed this year project into a game. The game simulates a pandemic situation, very much like the one we are seeing right now. As you have seen, real-time response is a critical component of handling a pandemic efficiently. 

It is by no means our intention to take the current epidemic lightly. However, we thought that this project assignment would allow to lighten the mood a little, as everyone's morale will also be taking a serious hit during this period of confinement. Keep your spirits high and make sure you give your courses your best (all of them, not just this one). We will need talented and bright engineers in the aftermath of this crisis.  

To play this game, you don't need any equipment other than the PSOC itself.
The game is entirely coded inside one FreeRTOS task (\textit{gameTask}).
It sends "events" and we ask you to make a code that will automatically respond to those "events".\\
Depending on your response time you will increase or not some variables.

\subsection*{Useful documentation:}
\begin{itemize}
    \item Official \rtos~ documentation: \url{https://www.freertos.org/Documentation/RTOS_book.html}
    \item Getting Started with PSoC 5LP: \url{https://www.cypress.com/file/41436/download}
    \item Video example on how to use the PSoC: \url{https://www.cypress.com/video-library/PSoC}
    \item The extension board schematics: \texttt{Extension\_PSoC.pdf}
		\item Getting started with the Logic Analyzer: \url{https://learn.sparkfun.com/tutorials/using-the-usb-logic-analyzer-with-sigrok-pulseview}
\end{itemize}
